\documentclass[11.5pt,a4paper]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{black}
\nopagenumbers{}
\usepackage[utf8]{inputenc}
\usepackage{ragged2e}
\usepackage[scale=0.915]{geometry}
\usepackage{import}
\usepackage{multicol}
\usepackage{import}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\name{\color{black}SREESHANTH\ }{\color{gray}THEKKEDATH}
\newcommand*{\customcventry}[7][.13em]{
\begin{tabular}{@{}l}
{\bfseries #4} \
{\itshape #3}
\end{tabular}
\hfill
\begin{tabular}{l@{}}
{\bfseries #6} \
{\itshape #2}
\end{tabular}
\ifx&#7&%
\else{\
\begin{minipage}{\maincolumnwidth}%
\small#7%
\end{minipage}}\fi%
\par\addvspace{#1}}
\begin{document}
\makecvtitle
\vspace*{-12mm}
\begin{center}\textbf{SOFTWARE ENGINEER}\end{center}
\begin{center}
\begin{tabular}{c c c}
\faMobile\enspace +91 9947242749& \enspace sreeshanththekkedath8@gmail.com & \enspace 
\faHome\enspace Kerala, INDIA\\
\faLinkedin\enspace \color{blue} \href{https://www.linkedin.com/in/sreeshanth-thekkedath-110393172/}{Sreeshanth Thekkedath}&
\faGithub\enspace \color{blue} \href{https://github.com/SreeshanthT}{github.com/SreeshanthT}& \end{tabular}
\end{center}

\section{Profile}
{Results-driven and versatile Software Engineer with proven expertise in Python, Django, Flask, and modern web technologies. I specialize in building robust, scalable, and secure web applications, leveraging both backend and frontend skills. Experienced in cloud solutions (AWS), DevOps practices, and automation, I deliver high-quality, maintainable code tailored to client needs. Adept at collaborating with global teams and clients, I am committed to exceeding expectations and driving business success through innovative technology solutions. Let’s work together to bring your ideas to life—on time and with excellence.}

\section{Areas of Expertise}
{Web development - Python - Django - Django Rest Framework - Flask - Jinja2 - GraphQL - AWS AppSync - REST API - MySQL/PostgreSQL - JavaScript - HTML/CSS/Bootstrap - React - Data Structure and Algorithm - Excel - GPT - Web Scrapping - AWS (Aurora, S3, Lambda, etc.) - Terraform - Docker - GitLab CI/CD - Pre-commit - Ruff - Trivy - SonarQube - nginx}
\section{Professional Experience}

\customcventry{12/2024 ‐ present}{{\color{blue}\href{https://www.trenser.com/}{(Trenser Technology Solutions)}}}{Software Engineer,}{Trivandrum, Kerala}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Developed and maintained Flask applications with Jinja2 templates, and created GraphQL APIs using AWS AppSync for dynamic and scalable web solutions.
\item Automated AWS resource provisioning and management using Terraform; containerized and deployed applications with Docker.
\item Built and optimized CI/CD pipelines with GitLab CI/CD, and implemented pre-commit hooks with Ruff linters to ensure code quality and consistency.
\item Utilized Trivy and SonarQube for vulnerability scanning and code analysis; worked extensively with AWS services including Aurora, S3, Lambda, and other core offerings.
\end{itemize}}}

\customcventry{02/2023 ‐ 12/2024}{{\color{blue}\href{https://reizend.in/}{(Reizend Private Limited)}}}{System Engineer,}{Kinfra, TVM}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Currently maintaining and developing a web application designed to manage sales data and analytics for business-to-business operations.
\item Performed server bug fixes and optimizations, enhancing the overall performance and reliability of the application. Utilized Python, Django, RestAPI, Django Rest Framework, HTML, CSS, and JavaScript in the development process.
\item Part of the server slowness diagnostic team, familiar with Linux-based servers and AWS environments. And conducted performance tuning of MySQL queries and implemented indexing strategies to improve database performance.
\item Created a comprehensive documentation library for Django applications using Sphinx, improving the efficiency of on-boarding and knowledge transfer. \color{blue}\href{https://pypi.org/project/dj-docs/}{dj-docs}
\end{itemize}}}

\customcventry{10/2021 ‐ 02/2023}{{\color{blue}\href{https://www.primalcodes.com/}{(Primalcodes Technology)}}}{Python Developer,}{West-hill, Calicut}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Contributed to the development of several e-commerce web applications and sales management applications.
\item Implemented RESTful APIs to support front-end functionality and ensure smooth data flow.
\item Developed a React-based e-commerce application, gaining familiarity with React and REST API development.
\item 
Gained knowledge in PostgreSQL database management as part of networking applications.
\end{itemize}}}

\section{Online Courses \& Certifications}
% \begin{multicols}{2}
{\begin{itemize}[label=\textbullet]
      \item Python Programming for Everybody \& Python Data Structures (AUG 2020) - University Of Michigan, Coursera
      \item Software Development React + NodeJS(Present), Crio.Do
  \end{itemize}} 
% \end{multicols}

\section{Education}
\customcventry{2017-2020}{APJ Abdul Kalam Technological University}{B-Tech}{College of Engineering, Vadakara}{}{
Electronics and Communication Engineering
}
    {Project — IoT Based Fault Detection In Powerline Transmission using Raspberry Pi.}
\section{Skills}
\begin{multicols}{2}
    {\begin{itemize}[label=\textbullet]
        \item {\textbf{Programming Languages: } Python, JavaScript}
        \vspace{-0.6\baselineskip} 
        \item {\textbf{Frameworks: } Django, React, Django Rest Framework}
        \vspace{-0.6\baselineskip} 
        \item {\textbf{Web Technologies: } HTML, CSS, Bootstrap}
        \vspace{-0.6\baselineskip} 
        \item {\textbf{Databases: } MySQL, PostgreSQL}
        \vspace{-0.6\baselineskip} 
        \item {\textbf{Tools \& Platforms: } PyCharm, VSCode, Git, AWS}
        \vspace{-0.6\baselineskip} 
        \item {\textbf{Other: } RESTful API, nginx}
    \end{itemize}}
\end{multicols}

% \section{Languages}
% \begin{multicols}{2}
%     \begin{itemize}[label=\textbullet]
%     \item {\textbf{Malayalam} [Native]}
%     \vspace{-0.5\baselineskip} 
%     \item \textbf{English} [Basic]\vspace{-0.5\baselineskip} 
%     \vspace{-0.5\baselineskip} 
%     \end{itemize}
% \end{multicols}
\end{document}